% !TEX root = main.tex
\section{Introduction}
\label{sec:Introduction}
When designing any radio communication system, trade-offs has to be made between bandwidth, power, system complexity and bit rate. For a given bandwidth and transmit power, the bit rate could be varied by using different modulation schemes. As higher order modulation schemes require higher $\nicefrac{E_b}{N_0}$, choosing optimum modulation scheme would require knowledge about the radio channel in order to maintain low enough BER at the receiver. This knowledge may be obtained by adding complexity in form of a feedback channel from receiver to transmitter. By performing some kind of error detection, the receiver may send information about detected error rates back to the transmitter. This enables the system to adapt the data rate to the state of the radio channel and thus provide better QoS for given power and bandwidth. 

In this paper, we present a radio communication system with this kind of feedback structure. The system is to be seen as a "proof of concept", and the goal is not to propose a complete radio system for commercial use. The adaptable quality is obtained by implementing a feedback path from the receiver to the transmitter using frequency-division duplexing (FDD). In this demonstration, we simulate the varying state of the radio channel by changing the transmit power for a more controllable and reproducible test environment.

Figure \ref{fig:block_toplevel} shows a top level block diagram of the proposed system. The figure shows that speech data is sent in the forward path from transmitter to receiver and the number of detected errors is sent in the feedback path from receiver to transmitter. The forward and feedback paths will be referred to as the \textit{data path} and the \textit{BER path} respectively. 
\input{block_top_level.tex}. 

\newpage
The proposed system is designed to switch between two different data rates, using two different modulation formats. Figure \ref{fig:concept} shows a qualitative illustration of the adaptive quality concept. The proposed system may be further improved by adding more levels, yielding even better utilization of available resources. 

\input{concept.tex}

Throughout this paper, we will use the word \textit{transmitter} when referring to the radio module that is transmitting the speech data and \textit{receiver} when referring to the module that is receiving it. This is not to be confused with the terms TX and RX, which we use when referring to the transmit and receive port on each radio module. 

The system is implemented using the software defined radio USRP-2901\cite{USRP2901} from National Instruments which contains all necessary RF hardware. All the software parts of the system is implementing in C++ and is executed on a standard personal computer. Pre-written C-libraries are used for the parts of the system concerning interface to the USRP, the computer sound card etc. These parts will not be explained in detail, but references to the libraries will be given. For the remaining parts of the system, we focus on explaining the implementation on a behavioural level and detailed descriptions of C code implementations is avoided. 

In section \ref{sec:specifications}, we present the system specifications and the link budget is presented in section \ref{sec:link_budget} together with associated measurements. A detailed description of the proposed system is given in section \ref{sec:design_description} and the motivation behind some crucial design decisions is presented in section \ref{sec:design_motivation}. Performed measurements is presented in section \ref{sec:verification} before a final conclusion is given in section \ref{sec:conclusion}.